### 2025-05-23 thesis/abs_en.tex
feat: polish23

To address these challenges, this thesis proposes and implements a cloud-based agricultural fruit weighing software system that integrates multi-protocol communication, image recognition, and data management. The system adopts a cloud-edge collaborative architecture: on the farm-side edge, fruit images and weight data are collected in real time, and a YOLO-based image recognition algorithm is used to identify fruit types before publishing the weighing messages. On the cloud side, these messages from electronic scales are subscribed to, followed by data processing and storage. The software supports multiple communication protocols, including MQTT, HTTP, and CoAP, ensuring compatibility with various types of weighing hardware for flexible integration and rapid deployment. A data management and visualization platform is developed using Spring Boot and Vue, offering efficient information management and multi-dimensional data visualization capabilities.

>>>>

To address these challenges, this thesis proposes and implements a cloud-based agricultural fruit weighing software system that integrates multi-protocol communication, image recognition, and data management. The system adopts a cloud-edge collaborative architecture: on the farm-side edge, fruit images and weight data are collected in real time, and a YOLO-based image recognition algorithm is used to identify fruit types before publishing the weighing messages. On the cloud side, these messages from electronic scales are subscribed to, followed by data processing and storage. The software supports multiple communication protocols, including MQTT, HTTP, and CoAP, ensuring compatibility with various types of weighing hardware for flexible integration and rapid deployment. A data management and visualization platform is developed using Spring Boot and Vue, offering efficient data management and insightful visual analytics.
